---
title: "GBLUP_h2"
author: "Ye Bi"
date: "`r Sys.Date()`"
output: html_document
---

```{r}
library(tidyverse)
library(ggplot2)
library(plyr)
library(ggpubr)
library(ggrepel)
library(tidyverse)
library(stargazer)
library(patchwork)
library(ggplot2)
```

## Drawing plots for h2, varE, varG
```{r}
source("functions.R")
met_names = met_name_func(mode = 'name')
```


```{r}
load_h2 = function(prepro, gblup){
  load(paste0("../temp/", prepro,"/", gblup, "/Control_",gblup,"_h2.rda" ))
  h2varcon <- as.data.frame(do.call(rbind, h2L))
  # h2varcon = h2varcon[-30,] #remove d3 from met. 
  load(paste0("../temp/", prepro,"/", gblup, "/Stress_",gblup,"_h2.rda" ))
  h2vartrt <- as.data.frame(do.call(rbind, h2L))
  # h2vartrt = h2vartrt[-30,]
  h2 = c(h2varcon$h2, h2vartrt$h2)
  varE = c(h2varcon$varE, h2vartrt$varE)
  varG = c(h2varcon$varG, h2vartrt$varG)
  df = data.frame(Met=met_names, 
                  h2=h2, 
                  varE = varE, 
                  varG = varG, 
                  Treatment = rep(c("Control", "Stress"), each=66))
  
  df.long <- reshape2::melt(df, id.vars = c('Met', 'Treatment'))
  
  
  h2.df.long <- df.long %>% filter(variable == 'h2') %>% droplevels()
  colnames(h2.df.long) <- c("Met", "Treatment", "variable", "value")
  h2.df.long$Treatment <- as.factor(h2.df.long$Treatment)
  h2.df.long$Met <- factor(h2.df.long$Met, levels=unique(h2.df.long$Met))
  h2.df.long$Kernel <- paste0(prepro, "-G-", gblup)
  return(h2.df.long)
}

h22L = list()
m= 1
for(i in c("log_lmer")){
  for(j in c("sommer")){
        h22L[[m]] = load_h2(i, j)
        m = m+1
  }
        }
```


###heritability plot
```{r}
H2h2.df.long <- rbind.data.frame(h22L[[1]])
my_colors <- RColorBrewer::brewer.pal(11, 'Spectral')[c(10,3)]
h2_scatter <- ggplot(H2h2.df.long, aes(x=Met, y=value)) + 
  geom_point(aes(colour=Treatment), size=2) +
  # geom_text(hjust=0, vjust=0, size = 2)+
  facet_grid(rows = vars(Treatment))+
  labs(x="Metabolite", y = "Heritability") +
  scale_y_continuous(limits=c(0, 1), breaks=c(0,0.2,0.4,0.6,0.8, 1)) +
  # theme_classic()+
  theme_bw()+
  scale_color_manual(values = my_colors)+
  theme(axis.text.x=element_text(size=8, angle=90, hjust=0.95, vjust=0.2),
        axis.text.y=element_text(size=8),
        axis.title.y = element_text(margin = margin(r=6)))
h2_scatter
# dev.print(pdf, file="../temp/h2_scatter_plot.pdf", height=6, width=10)
```



```{r}
comp_h2 = compare_plot_generator(df = H2h2.df.long, 
                       up_thr = 0.02, 
                       low_thr = 0.2,
                       limits_range = c(0,0.8),
                       breaks_range = seq(0,0.8,0.1))
comp_h2
# dev.print(pdf, file="../temp/h2_compare.pdf", height=8, width=8)
```


## h2 density plot
```{r}
df = h22L[[1]]
h2_density = density_plot_generator(df = df,
                      my_colors=RColorBrewer::brewer.pal(11, 'Spectral')[c(10,3)],
                      limits_range = c(0,1),
                      breaks_range = seq(0,1,0.2),
                      x_name = "Heritability",
                      ylim = NULL,
                      lines = T)
h2_density
# dev.print(pdf, file=paste0("../temp/h2_density.pdf"), height=4, width=8)
```
```{r}
ggarrange(h2_scatter,  
          NULL,
          ggarrange(h2_density, comp_h2,
                    ncol = 2, labels = c("(B)", "(C)"), 
                    vjust=-0.1, 
                    common.legend = F,
                    widths = c(1.2, 1)), 
          nrow = 3, 
          labels = c("(A)", ""), vjust=1.2, hjust=0,
          heights = c(1.8, 0.1, 1),# Labels of the scatter plot
          common.legend = F ) 
dev.print(pdf, file=paste0("../temp/h2_plots.pdf"), height=10, width=10)
```



## h2 density plot --- FA
```{r}
####functions.R
FA_h2_den=FA_density_plot_generator(df=h22L[[1]],
                          my_colors = RColorBrewer::brewer.pal(11, 'Spectral')[c(11,10,9,8,7,5,4,3,2,1)],
                          limits_range = c(0,1),
                          breaks_range = seq(0,1,0.2),
                          x_name = "Heritability", 
                          ylim = NULL)
FA_h2_den
# dev.print(pdf, file=paste0("../temp/FA_h2_density.pdf"), height=4, width=8)
```



##Loading pred corr 
```{r}
path.bglr = "../ARC_outputs/Met_same_genotypes_per_treatment/GBLUP/outputs_GBLUP/"
PreCorr = load_pred_corr_func(path=path.bglr, kernel = "BGLR", namm=NULL)
# PreCorr = PreCorr %>% filter(Met != "ribitol")%>% droplevels()


path.GK = "../ARC_outputs/Met_same_genotypes_per_treatment/GK/outputs_GK/"
PreCorr_GK = load_pred_corr_func(path=path.GK, kernel = "GK", namm=NULL)
# PreCorr_GK = PreCorr_GK %>% filter(Met != "ribitol") %>% droplevels()
```

```{r}
VGG16_RF = list()
m = 1
for (i in seq(10,100,10)){
  path = paste0("../ARC_outputs/Met_same_genotypes_per_treatment/DLs_RF/VGG16_cv", i, ".csv")
  vgg_rr1 = read.csv(path)
  VGG16_RF[[m]] = vgg_rr1
  m = m+1
}
VGG16_RF = do.call(rbind, VGG16_RF)
```



```{r}
# VGG16_RR_1 = DLs_RR_reader("VGG16", 1)
# VGG16_RR_100 = DLs_RR_reader("VGG16", 100)
# VGG16_RR_1000 = DLs_RR_reader("VGG16", 1000)
# VGG16_RR_10000 = DLs_RR_reader("VGG16", 10000)
# PreCorr_vgg16_RR_1 = DL_extractor_func(df = VGG16_RR_1, met_names, "VGG16_RR_1")
# PreCorr_vgg16_RR_100 = DL_extractor_func(df = VGG16_RR_100, met_names, "VGG16_RR_100")
# PreCorr_vgg16_RR_1000 = DL_extractor_func(df = VGG16_RR_1000, met_names, "VGG16_RR_1000")
# PreCorr_vgg16_RR_10000 = DL_extractor_func(df = VGG16_RR_10000, met_names, "VGG16_RR_10000")
# 
# ResNet50_RR_1 = DLs_RR_reader("ResNet50", 1)
# ResNet50_RR_100 = DLs_RR_reader("ResNet50", 100)
# ResNet50_RR_1000 = DLs_RR_reader("ResNet50", 1000)
# ResNet50_RR_10000 = DLs_RR_reader("ResNet50", 10000)
# PreCorr_ResNet50_RR_1 = DL_extractor_func(df = ResNet50_RR_1, met_names, "ResNet50_RR_1")
# PreCorr_ResNet50_RR_100 = DL_extractor_func(df = ResNet50_RR_100, met_names, "ResNet50_RR_100")
# PreCorr_ResNet50_RR_1000 = DL_extractor_func(df = ResNet50_RR_1000, met_names, "ResNet50_RR_1000")
# PreCorr_ResNet50_RR_10000 = DL_extractor_func(df = ResNet50_RR_10000, met_names, "ResNet50_RR_10000")
# 
# 
# EfficientNetB7_RR_1 = DLs_RR_reader("EfficientNetB7", 1)
# EfficientNetB7_RR_100 = DLs_RR_reader("EfficientNetB7", 100)
# EfficientNetB7_RR_1000 = DLs_RR_reader("EfficientNetB7", 1000)
# EfficientNetB7_RR_10000 = DLs_RR_reader("EfficientNetB7", 10000)
# PreCorr_EfficientNetB7_RR_1 = DL_extractor_func(df = EfficientNetB7_RR_1, met_names, "EfficientNetB7_RR_1")
# PreCorr_EfficientNetB7_RR_100 = DL_extractor_func(df = EfficientNetB7_RR_100, met_names, "EfficientNetB7_RR_100")
# PreCorr_EfficientNetB7_RR_1000 = DL_extractor_func(df = EfficientNetB7_RR_1000, met_names, "EfficientNetB7_RR_1000")
# PreCorr_EfficientNetB7_RR_10000 = DL_extractor_func(df = EfficientNetB7_RR_10000, met_names, "EfficientNetB7_RR_10000")

```


```{r}
# VGG16 <- read.csv("../temp/DLs/VGG16.csv")
# PreCorr_vgg16 = DL_extractor_func(df = VGG16, met_names, "VGG16")
# 
# 
# VGG16_RR <- read.csv("../temp/DLs/VGG16_RidgeRegression.csv") 
# PreCorr_vgg16_RR = DL_extractor_func(df = VGG16_RR, met_names, "VGG16_RR")
# # PreCorr_vgg16_RF = DL_extractor_func(df = VGG16_RF, met_names, "VGG16_RF")
# 
# ResNet <- read.csv("../temp/DLs/ResNet50.csv")
# PreCorr_resnet = DL_extractor_func(df = ResNet, met_names, "ResNet")
# 
# Eff <- read.csv("../temp/DLs/EfficientNetB7.csv")
# PreCorr_eff = DL_extractor_func(df = Eff, met_names, "Eff")
```

```{r}
# path.GK0 = "../ARC_outputs/Met_same_genotypes_per_treatment/GK/outputs_GK_ori/"
# PreCorr_GK0 = load_pred_corr_func(path=path.GK0, kernel = "GK0", namm=NULL)
```

## density plot for bglr-G predcorr
```{r}
mu_perMet = ddply(PreCorr, c("Treatment", 'Met'), summarise, value=mean(Corr, na.rm=T))
Pred_Corr_dens = density_plot_generator(df=mu_perMet, 
                       my_colors=RColorBrewer::brewer.pal(11, 'Spectral')[c(10,3)],
                       limits_range = c(-0.2,1),
                       breaks_range = seq(-0.2,1,0.2), 
                       x_name = "Prediction accuracy",
                       ylim = NULL,
                       lines = T)
Pred_Corr_dens
# dev.print(pdf, file=paste0("../temp/BGLR_G_PredCorr_density.pdf"), height=4, width=8)
```

```{r}
comp_PreCorr = compare_plot_generator(df = mu_perMet, 
                       up_thr = 0.02, 
                       low_thr = 0.15,
                       limits_range = c(0,0.7),
                       breaks_range = seq(0,0.7,0.1))

comp_PreCorr
# dev.print(pdf, file="../temp/Precorr_compare.pdf", height=8, width=8)
```

## FA_summary
```{r}
h2_FA_summ = FA_summary_func(df = h22L[[1]])
ggcorr_FA_summ = FA_summary_func(df = df_ggcorr)
corr_FA_summ = FA_summary_func(df = mu_perMet)

```


##FA Pred corr density plot
```{r}
mu_perMet = ddply(PreCorr, c("Treatment", 'Met'), summarise, value=mean(Corr, na.rm=T))
df = mu_perMet


FA_PreCorr_GBLUP_den=FA_density_plot_generator(df=mu_perMet,
                                                my_colors = RColorBrewer::brewer.pal(11, 'Spectral')[c(11,10,9,8,7,5,4,3,2,1)],
                                                limits_range = c(0, 1),
                                                breaks_range = seq(0,1,0.2),
                                                x_name = "Prediction accuracy",
                                                ylim = NULL)
  
FA_PreCorr_GBLUP_den
# dev.print(pdf, file=paste0("../temp/FA_BGLR_G_PredCorr_density.pdf"), height=4, width=8)
```


```{r}
ggarrange(FA_h2_den, 
          FA_PreCorr_GBLUP_den, 
          nrow = 2, 
          labels = c("(A)", "(B)"), 
          vjust=-0.1, 
          common.legend = T)

dev.print(pdf, file="../temp/FA_h2_Precorr.pdf", height =9, width = 7)
```


# ######Boxplot for PredCorr BGLR-G
```{r}
library(plyr)
# df = vgg
# df$Corr = vgg$value

df = PreCorr
mu <- ddply(df, "Treatment", summarise, corr.mean=mean(Corr, na.rm=T))
head(mu)

my_colors <- RColorBrewer::brewer.pal(11, 'Spectral')[c(10, 3)]

Pred_Cor_boxplot <- ggplot(df, aes(x=Met, y=Corr)) + 
           facet_grid(rows = vars(Treatment))+
           geom_boxplot(aes(fill=Treatment), outlier.size=0.5, outlier.alpha = 0.7, lwd=0.3)+
           labs(x="Metabolite", y = "Prediction accuracy") +
           theme_bw()+
           geom_hline(data=mu, aes(yintercept=corr.mean, color=Treatment), linetype='solid', linewidth = 1)+
           scale_y_continuous(limits=c(-0.6, 0.9), breaks=c(-0.6,-0.4,-0.2, 0, 0.2,0.4,0.6, 0.8, 1)) +
           scale_fill_manual(values = ggplot2::alpha(my_colors, 0.7))+
           scale_color_manual(values = my_colors)+
           theme(axis.text.x=element_text(size=8, angle=90, hjust=0.95, vjust=0.2),
                 axis.text.y=element_text(size=8))


Pred_Cor_boxplot
# dev.print(pdf, file="../temp/boxplot_BGLR_G.pdf", height = 6, width = 10)
```

```{r}
library(ggpubr)
ggarrange(Pred_Cor_boxplot,  
          NULL,
          ggarrange(Pred_Corr_dens, comp_PreCorr,
                    ncol = 2, labels = c("(B)", "(C)"), 
                    vjust=-0.1, 
                    common.legend = F,
                    widths = c(1.2, 1)), 
          nrow = 3, 
          labels = c("(A)", ""), vjust=1.5, hjust=0,
          heights = c(1.8, 0.1, 1),# Labels of the scatter plot
          common.legend = F ) 
# ggarrange(Pred_Cor_boxplot, 
#           NULL,
#           Pred_Corr_dens, 
#           nrow = 3, 
#           heights = c(3,0.2,1),
#           labels = c("(A)","", "(B)"), 
#           vjust=-0.1, 
#           common.legend = T)
dev.print(pdf, file="../temp/GBLUP_plots.pdf", height=10, width=10)
```

# ###### Boxplot to compare models
```{r}
# combb = rbind.data.frame(PreCorr, 
#                          # PreCorr_vgg16_RF)
#                          PreCorr_vgg16,
#                          PreCorr_vgg16_RR,
#                          PreCorr_vgg16_RF,
#                          PreCorr_resnet,
#                          PreCorr_eff)
# 
# my_colors <- RColorBrewer::brewer.pal(11, 'Spectral')[c(10, 9,8, 4, 3, 2)]
# 
# lmmm = c(min(combb$Corr), max(combb$Corr))
# 
# dp10 <- ggplot(combb, aes(x=Met, y=Corr)) +
#            facet_grid(rows = vars(Treatment))+
#            geom_boxplot(aes(fill=Kernel), outlier.size=0.5, outlier.alpha = 0.7, lwd=0.2)+
#            labs(x="Metabolite", y = "Predictive correlation") +
#            theme_bw()+
#            scale_y_continuous(limits=c(-0.61, 0.90), breaks=seq(-0.60, 0.90, 0.2)) +
#            scale_fill_manual(values = ggplot2::alpha(my_colors, 0.7))+
#            theme(axis.text.x=element_text(size=8, angle=90, hjust=0.95, vjust=0.2),
#                  axis.text.y=element_text(size=8))+
#            # geom_hline(data=mu, aes(yintercept=corr.mean, color=Treatment), linetype='solid', linewidth = 1)+
#            scale_color_manual(values = my_colors)
# 
# 
# dp10
# dev.print(pdf, file="../temp/DLs_boxplot.pdf", height = 10, width = 20)
```


#### Barplot
- BGLR_G
- BGLR_GK
- Mega_G
- Mega_GK
```{r}
# vgg16_RR_1_mu <- pred_mean_generator(PreCorr_vgg16_RR_1)
# vgg16_RR_100_mu <- pred_mean_generator(PreCorr_vgg16_RR_100)
# vgg16_RR_1000_mu <- pred_mean_generator(PreCorr_vgg16_RR_1000)
# vgg16_RR_10000_mu <- pred_mean_generator(PreCorr_vgg16_RR_10000)
# vgg16_RR_comp = cbind(vgg16_RR_1_mu$corr.mean,
#                       vgg16_RR_100_mu$corr.mean,
#                       vgg16_RR_1000_mu$corr.mean,
#                       vgg16_RR_10000_mu$corr.mean)
# 
# vgg16_RR_mu = apply(vgg16_RR_comp, 1, max)
# vgg16_RR_mu = cbind.data.frame(vgg16_RR_1_mu[,1:2],
#                            corr.mean = vgg16_RR_mu)
# 
# 
# ResNet50_RR_1_mu <- pred_mean_generator(PreCorr_ResNet50_RR_1)
# ResNet50_RR_100_mu <- pred_mean_generator(PreCorr_ResNet50_RR_100)
# ResNet50_RR_1000_mu <- pred_mean_generator(PreCorr_ResNet50_RR_1000)
# ResNet50_RR_10000_mu <- pred_mean_generator(PreCorr_ResNet50_RR_10000)
# ResNet50_RR_comp = cbind(ResNet50_RR_1_mu$corr.mean,
#                       ResNet50_RR_100_mu$corr.mean,
#                       ResNet50_RR_1000_mu$corr.mean,
#                       ResNet50_RR_10000_mu$corr.mean)
# 
# ResNet50_RR_mu = apply(ResNet50_RR_comp, 1, max)
# ResNet50_RR_mu = cbind.data.frame(ResNet50_RR_1_mu[,1:2],
#                            corr.mean = ResNet50_RR_mu)
# 
# EfficientNetB7_RR_1_mu <- pred_mean_generator(PreCorr_EfficientNetB7_RR_1)
# EfficientNetB7_RR_100_mu <- pred_mean_generator(PreCorr_EfficientNetB7_RR_100)
# EfficientNetB7_RR_1000_mu <- pred_mean_generator(PreCorr_EfficientNetB7_RR_1000)
# EfficientNetB7_RR_10000_mu <- pred_mean_generator(PreCorr_EfficientNetB7_RR_10000)
# EfficientNetB7_RR_comp = cbind(EfficientNetB7_RR_1_mu$corr.mean,
#                       EfficientNetB7_RR_100_mu$corr.mean,
#                       EfficientNetB7_RR_1000_mu$corr.mean,
#                       EfficientNetB7_RR_10000_mu$corr.mean)
# 
# EfficientNetB7_RR_mu = apply(EfficientNetB7_RR_comp, 1, max)
# EfficientNetB7_RR_mu = cbind.data.frame(EfficientNetB7_RR_1_mu[,1:2],
#                            corr.mean = EfficientNetB7_RR_mu)
```

```{r}
# vgg_mu <- pred_mean_generator(PreCorr_vgg16)
# vgg_mu_RR <- pred_mean_generator(PreCorr_vgg16_RR)
# vgg_mu_RF <- pred_mean_generator(PreCorr_vgg16_RF)
# resnet_mu <- pred_mean_generator(PreCorr_resnet)
# eff_mu <- pred_mean_generator(PreCorr_eff)
```

```{r}
DLs_model_names = c("VGG16", "ResNet50", "EfficientNetB7","InceptionV3", "MobileNetV2", "DenseNet201")
DLs_RR_mu_L = list()
PreCorr_DL_L = list()
for (i in 1:6){
  model_name = DLs_model_names[i]
  DLs_RR_mu_L[[i]] = DLs_RR_mu_generator(model = model_name)
  PreCorr_DL_L[[i]] = DLs_RR_PreCorr_generator(model = model_name)
}
names(DLs_RR_mu_L) = DLs_model_names
names(PreCorr_DL_L) = DLs_model_names
```

```{r}
BGLR_G_mu <- pred_mean_generator(PreCorr)
BGLR_GK_mu <- pred_mean_generator(PreCorr_GK) 
mega_G_mu <- pred_mean_generator(PreCorr_mega_G) #MegaLMM_test.Rmd

mega_GK_mu0.2 <- pred_mean_generator(PreCorr0.2) #GK.Rmd
mega_GK_mu0.4 <- pred_mean_generator(PreCorr0.4)
mega_GK_mu0.6 <- pred_mean_generator(PreCorr0.6)
mega_GK_mu0.8 <- pred_mean_generator(PreCorr0.8)

mega_GK_comp = cbind(GK0.2 = mega_GK_mu0.2$corr.mean,
                     GK0.4 = mega_GK_mu0.4$corr.mean,
                     GK0.6 = mega_GK_mu0.6$corr.mean,
                     GK0.8 = mega_GK_mu0.8$corr.mean)
mega_GK_mu = apply(mega_GK_comp, 1, max)
mega_GK_mu = cbind.data.frame(mega_GK_mu0.2[,1:2],
                           corr.mean = mega_GK_mu)
```

```{r}

```

```{r}
# mm <- plyr::ddply(G_GK_dff, c("Treatment"), summarise, corr.mean=mean(Corr_diff, na.rm=T), corr.me = median(Corr_diff, na.rm=T))
BGLR_G_mu$corr.mean[BGLR_G_mu$corr.mean < 0.1]=0

DLs_model_names_selected = c("VGG16", "ResNet50", "EfficientNetB7","InceptionV3", "MobileNetV2", "DenseNet201")
dff_DLs_L = list()
for (i in 1:length(DLs_model_names_selected)){
  dff_DLs_L[[i]] = pred_dff_generator(df1 = BGLR_G_mu,
                                     df2 = DLs_RR_mu_L[[DLs_model_names_selected[i]]],
                                     Method=DLs_model_names_selected[i])
}

# dff_vgg=pred_dff_generator(df1=BGLR_G_mu, 
#                    df2=vgg16_RR_mu, 
#                    Method="VGG")
# 
# dff_resnet=pred_dff_generator(df1=BGLR_G_mu, 
#                    df2=ResNet50_RR_mu, 
#                    Method="ResNet")
# dff_eff=pred_dff_generator(df1=BGLR_G_mu, 
#                    df2=EfficientNetB7_RR_mu, 
#                    Method="EfficientNet")
# 
dff_bglr_gk=pred_dff_generator(df1=BGLR_G_mu,
                   df2=BGLR_GK_mu,
                   Method="RKHS")
dff_gblup = pred_dff_generator(df1=BGLR_G_mu,
                               df2=BGLR_G_mu,
                               Method="GBLUP")  
my_colors <- RColorBrewer::brewer.pal(11, 'Spectral')[c(1:4, 9:11)]
ccc = rbind(do.call(rbind, dff_DLs_L),
            dff_bglr_gk)
            
ccc$Method = factor(ccc$Method, levels=c(DLs_model_names, "RKHS", "GBLUP"))

ttt = ccc[!is.infinite(ccc$value), ]
ttt = ttt %>% filter(value >= 0) %>% droplevels()
limm = c(floor(min(ttt$value)), ceiling(max(ttt$value)))
dp_diff <- ggplot(ttt, aes(y=value, x=Met, fill=Method)) +
            # geom_line()+
            geom_bar(stat="identity",position="dodge", width = 1)+
            facet_grid(rows = vars(Treatment))+
            labs(x="Metabolite", y = "Percentage difference (%)") +
            theme_bw()+
            geom_hline(aes(yintercept = 0), color = 'darkgrey', linetype='solid', linewidth = 0.3)+
            # scale_y_continuous(limits=c(0, 90), breaks=seq(0,90,10)) +
            # scale_y_continuous(limits=c(0,400)) +
            scale_fill_manual(values = alpha(my_colors, 1))+
            # scale_color_manual(values = my_colors)+
            theme(axis.text.x=element_text(size=8, angle=90, hjust=0.95, vjust=0.2),
                  axis.text.y=element_text(size=8))

# dp_diff <- ggplot(ttt, aes(y=Met, x=value, fill=Method)) +
#             # geom_line()+
#             geom_bar(stat="identity",position="dodge")+
#             facet_grid(cols = vars(Treatment))+
#             labs(x="Metabolite", y = "Percentage difference (%)") +
#             theme_bw()+
#             geom_vline(aes(xintercept = 0), color = 'darkgrey', linetype='solid', linewidth = 0.3)+
#             scale_x_continuous(limits=c(0, 90), breaks=seq(-160,90,50)) +
#             # scale_y_continuous(limits=c(0,400)) +
#             scale_fill_manual(values = alpha(my_colors, 1))+
#             # scale_color_manual(values = my_colors)+
#             theme(axis.text.x=element_text(size=8, angle=90, hjust=0.95, vjust=0.2),
#                   axis.text.y=element_text(size=8))

dp_diff
# dev.print(pdf, file="../temp/DL_dff_barplot_0.1_positive.pdf", height = 6, width = 10)

# dev.print(pdf, file="../temp/DL_dff_barplot_0.1.pdf", height = 6, width = 10)
# summary(ccc$value)
```

```{r}
# mm <- plyr::ddply(G_GK_dff, c("Treatment"), summarise, corr.mean=mean(Corr_diff, na.rm=T), corr.me = median(Corr_diff, na.rm=T))
BGLR_G_mu$corr.mean[BGLR_G_mu$corr.mean < 0.1]=0
dff_bglr_gk=pred_dff_generator(df1=BGLR_G_mu, 
                   df2=BGLR_GK_mu, 
                   Method="RKHS")
dff_mega_g=pred_dff_generator(df1=BGLR_G_mu, 
                   df2=mega_G_mu, 
                   Method="MegaLMM-G")
dff_mega_gk=pred_dff_generator(df1=BGLR_G_mu, 
                   df2=mega_GK_mu, 
                   Method="MegaLMM-GK")
  
my_colors <- RColorBrewer::brewer.pal(11, 'PiYG')[c(9,  2)]

ccc = rbind(dff_mega_g, dff_mega_gk)
ccc$Method = factor(ccc$Method, levels=c("RKHS", "MegaLMM-G", "MegaLMM-GK"))

ttt = ccc[!is.infinite(ccc$value), ]
ttt = ttt %>% filter(value >= 0) %>% droplevels()
limm = c(floor(min(ttt$value)), ceiling(max(ttt$value)))

dp_diff <- ggplot(ttt, aes(x=Met, y=value, fill=Method)) + 
            geom_bar(stat="identity",position="dodge")+
            facet_grid(rows = vars(Treatment))+
            labs(x="Metabolite", y = "Percentage difference (%)") +
            theme_bw()+
            geom_hline(aes(yintercept = 0), color = 'grey', linetype='solid', linewidth = 0.3)+
            scale_y_continuous(limits=c(-25, 50), breaks=seq(-30,50,10)) +
            scale_fill_manual(values = alpha(my_colors, 0.8))+
            # scale_color_manual(values = my_colors)+
            theme(axis.text.x=element_text(size=8, angle=90, hjust=0.95, vjust=0.2),
                  axis.text.y=element_text(size=8),
                  axis.title.y = element_text(margin = margin(r=6)),
                  legend.position = "right")

dp_diff

# dev.print(pdf, file="../temp/mega_bglr_diff_barplot.pdf", height = 6, width = 20)
```

### density plot to BGLR-G v.s. BGLR-GK
```{r}
my_colors <- RColorBrewer::brewer.pal(11, 'Spectral')[c(10,3)]


# dff_bglr_gk_dens=density_plot_generator(df=dff_bglr_gk, 
#                        my_colors=my_colors,
#                        limits_range = c(-40,40),
#                        breaks_range = seq(-40,40,10), 
#                        x_name = "Percentage difference (%)",
#                        lines = F,
#                        ylim = c(0, 0.2))

dff_mega_g_dens=density_plot_generator(df=dff_mega_g, 
                       my_colors=my_colors,
                       limits_range = c(-40,40),
                       breaks_range = seq(-40,40,10),  
                       x_name = "Percentage difference (%)",
                       lines = F,
                       ylim = c(0, 0.2))

dff_mega_gkk_dens=density_plot_generator(df=dff_mega_gk, 
                       my_colors=my_colors,
                       limits_range = c(-40,40),
                       breaks_range = seq(-40,40,10),  
                       x_name = "Percentage difference (%)",
                       lines = F,
                       ylim = c(0, 0.2))
  
  
# print(p33)
# dev.print(pdf, file=paste0("../temp/G_GK_PredCorr_density.pdf"), height=4, width=8)
```
```{r}
library(ggpubr)

ggarrange(dp_diff, 
          NULL,
          ggarrange(dff_mega_g_dens, dff_mega_gkk_dens,
                    ncol = 2, labels = c("(B)", "(C)"), 
                    vjust=-0.1, 
                    common.legend = T,
                    legend = "right"), 
          nrow = 3, 
          labels = "(A)",vjust=1.5, hjust=0,
          heights = c(2, 0.1, 1)) 

dev.print(pdf, file="../temp/G_GK_Mega.pdf", height = 10, width = 10)
```



### FA density plot: BGLR-GK, mega-G, mega-GK
```{r}
dff_bglr_gk_FAdens=FA_density_plot_generator(dff_bglr_gk,
                                     # my_colors,
                                     limits_range = c(-30,30),
                                     breaks_range = seq(-30,30,10),
                                     x_name = "Percentage difference (%)",
                                     ylim = NULL)
dff_mega_g_FAdens=FA_density_plot_generator(dff_mega_g,
                                     # my_colors,
                                     limits_range = c(-30,30),
                                     breaks_range = seq(-30,30,10),
                                     x_name = "Percentage difference (%)",
                                     ylim = NULL)
dff_mega_gk_FAdens=FA_density_plot_generator(dff_mega_gk,
                                     # my_colors,
                                     limits_range = c(-30,30),
                                     breaks_range = seq(-30,30,10),
                                     x_name = "Percentage difference (%)",
                                     ylim = NULL)
```
```{r}
library(ggpubr)
ggarrange(dff_bglr_gk_FAdens, dff_mega_g_FAdens, dff_mega_gk_FAdens,
                    nrow = 3, labels = c("(A)", "(B)", "(C)"), vjust=-0.1, common.legend = T)

dev.print(pdf, file="../temp/FA_dens_BGLR_Mega.pdf", height =14, width = 7)
```
```{r}
FA_summary_func(df=dff_bglr_gk)
FA_summary_func(df=dff_mega_g)
FA_summary_func(df=dff_mega_gk)
```




################################################################################################################################################
#Testing diff R2 in BGLR
```{r, eval = F}
# # path.bglr = "../ARC_outputs/GBLUP_whole/outputs_GBLUP/"
# # path.bglr = "../ARC_outputs/BGLR_R2/outputs/"
# # met2remove = c(13,28,30,38,62,67)
# # met_names0 <- read.delim("../Met/raw_data/met_names.txt", header=FALSE)
# # met_names = met_names0[-met2remove, 1]
# 
# load_r2_pred_corr_func <- function(path, R2, met2remove){
#           bglr_conL <- list()
#           bglr_trtL <- list()
#           for (i in 1:100){
#             bglr_conL[[i]] <- readRDS(file=file.path(path.bglr,paste0(R2 ,"/Control_bglr_r2_", R2,"_cv_",i,".RDS")))
#             bglr_trtL[[i]] <- readRDS(file=file.path(path.bglr,paste0(R2 ,"/Stress_bglr_r2_", R2,"_cv_",i,".RDS")))
#           }
#           
#           bglr.c.df <- do.call(rbind, bglr_conL)
#           bglr.c.df = bglr.c.df[, -met2remove]
#           colnames(bglr.c.df)= met_names
#           
#           bglr.t.df <- do.call(rbind, bglr_trtL)
#           bglr.t.df = bglr.t.df[, -met2remove]
#           
#           colnames(bglr.t.df) = met_names
#           
#           
#           temp1 <- reshape2::melt(bglr.c.df)
#           temp2 <- reshape2::melt(bglr.t.df)
#           temp3 <- rbind.data.frame(temp1,temp2)
#           temp3$group <- rep(c("Control", "Stress"), each = 6700)
#           colnames(temp3) <- c("CV", "Met", "Corr", "Treatment")
#           temp3$Kernel = paste0("BGLR-r2-", R2)
#           
#           return(temp3)
#     }
```

```{r, eval=F}
# predCorr_0.05 = load_r2_pred_corr_func(path=path.bglr, R2=0.05, met2remove = met2remove)
# predCorr_0.1 = load_r2_pred_corr_func(path=path.bglr, R2=0.1, met2remove = met2remove)
# predCorr_0.3 = load_r2_pred_corr_func(path=path.bglr, R2=0.3, met2remove = met2remove)
```

## point plot for h2 v.s. PredCorr
```{r}
# somm_h2 = h22L[[1]]
# somm_h2 = somm_h2[,-c(3,5)]
# bglr_mu_perMet = mu_perMet
# bglr_mu_perMet$Treatment=gsub("HNT", "Stress", bglr_mu_perMet$Treatment)
# #cobine h2 and predCorr_mean values into one dataframe.
# bglr_h2_predCorr = merge(somm_h2, bglr_mu_perMet, by = c('Met','Treatment'))
# 
# df = bglr_h2_predCorr
# # library(plyr)
# rr2 <- ddply(df, "Treatment", summarise, r2 = cor(h2, corr.mean^2, use = "complete.obs")^2)
# 
# # df.con = df[df$Treatment == "Control", ]
# # df.trt = df[df$Treatment == "Stress", ]
# # 
# # summary(lm(data=df.con, h2~corr.mean))$r.squared
# # summary(lm(data=df.trt, h2~corr.mean))$r.squared
# 
# my_colors <- RColorBrewer::brewer.pal(11, 'Spectral')[c(10, 3)]
# 
# ggplot(bglr_h2_predCorr, aes(x=h2, y=corr.mean^2, color=Treatment))+
#   geom_point(size = 2)+
#   facet_grid(rows = vars(Treatment))+
#   labs(x="Heritability", y = "R2") +
#   scale_y_continuous(limits=c(0, 1), breaks=c(0, 0.2,0.4,0.6,0.8, 1)) +
#   theme_bw()+
#   scale_color_manual(values = my_colors)+
#   geom_abline(intercept = 0, slope = 1, linewidth = 0.3, color='red') 
# 
# dev.print(pdf, file="../temp/bglr_h2_r2.pdf", height = 6, width = 10)

```

## stacked barplot for varE varG 
```{r}
# var.df.long <- df.long %>% filter(variable != 'h2') %>% droplevels()
# colnames(var.df.long) = c("Met", "Treatment", "Var", "value")
# var.df.long$Treatment <- as.factor(var.df.long$Treatment)
# var.df.long$Met <- factor(var.df.long$Met, levels=unique(var.df.long$Met))
# var.df.long$Var <- factor(var.df.long$Var, levels=c("varE", "varG"))
# 
# my_colors <- RColorBrewer::brewer.pal(9, 'Pastel1')[c(1, 3)]
# ggplot(var.df.long, aes(x = Met, y = value, fill=Var)) +
#   geom_col(position = "fill")+
#   facet_grid(rows = vars(Treatment))+
#   theme_classic()+
#   labs(x="Metabolite", y = "Variance component") +
#   scale_fill_manual(values = my_colors)+
#   theme(axis.text.x=element_text(size=8, angle=90, hjust=0.95, vjust=0.2),
#         axis.text.y=element_text(size=8))
# dev.print(pdf, file="../outputs/GBLUP_whole/var.pdf", height=6, width=10)
```